Informing policy via dynamic models: Eliminating cholera in Haiti

### 2022-09-22 ms.Rnw
Minor edit

While dynamic models may potentially result in meaningful scientific insights, one must be careful not to assume the results of a single analysis as a de-facto feature of the system.
It is important instead to recognize and assess the modeling simplifications and assumptions that were used in order to arrive at the conclusions.
In epidemiological studies, for example, it is unreasonable to expect that our quantitative understanding of individual-level processes will perfectly match model parameters that were fit to population-level case counts \jwc{REF??},
making direct interpretation estimated parameters difficult.

>>>>

While dynamic models may potentially result in meaningful scientific insights, one must be careful not to assume the results of a single analysis as a de-facto feature of the system.
It is important instead to recognize and assess the modeling simplifications and assumptions that were used in order to arrive at the conclusions.
In epidemiological studies, for example, it is unreasonable to expect that our quantitative understanding of individual-level processes will perfectly match model parameters that were fit to population-level case counts \citep{he10} \jwc{ED: ARE THERE BETTER REFERENCES FOR THIS?},
making direct interpretation estimated parameters difficult.
